The connection between star formation rate and dark matter halo mass in the epoch of reionization

### 2015-04-29 paper/ms.tex
new pass on the abstract. first pass on results

\keywords{galaxies: high-redshift --- methods: numerical} 
\begin{abstract}
We present updated constraints on the relationship between the star
formation rate and dark matter halo mass at redshift $z\sim 6$.
The observational basis for our work is the restframe UV luminosity
function data obtained with CFHTLS, HST Legacy Survey and UKIDSS.
The constraints are based on an abundance matching methodology to the
observational data using cosmological N-body simulations.
We also take into account the influence on the results of the dust extinction
scaling derived from observations by Bouwens.
We show dependence of our parameter uncertainties related to the
comoving volume and magnitude range in observed surveys, taking advantage of the 
wide mass resolution range of latest available dark matter halo catalogs.
We compare our results against the results of abundance matching
methods (to the stellar mass), a semi-analytic model of galaxy
formation (GALFORM) and a hydrodynamical simulation (Illustris).
\end{abstract}

@@

We performed MCMC runnings with 100.000 steps over the 64 small 
cubic boxes (of $250$ \hMpc side length) fitting the LF to the 
Willott observational data, comparing the two cases; with and 
without dust attenuation. (figures \ref{fig:OD1_MCMC_best_steps_w} and 
\ref{fig:OD1_MCMC_best_steps_wo}). 
We used the Likelihood Ratio criterion ($\mathcal{LR}= 0.5$) to
define the $1\sigma$ confidence interval for our parameters.

$M_0$ is quite similar in booth cases (they are compatible within 
the error bars), the turnover point corresponds to the same mass.
$\gamma$ and $L_0$ shown a significative difference in booth cases.
$\beta$ is hard to constraint in booth cases. 
The parameer was limited to vary in the range form 0.0 to 1.6. 
$1\sigma$ region covers the whole range.

>>>>

\keywords{galaxies: high-redshift --- methods: numerical} 
\begin{abstract}
We present updated constraints on the relationship between the star
formation rate and dark matter halo mass at redshift $z\sim 6$.
The observational basis for our work is the restframe UV luminosity
function data obtained with HST, CFHTLS, Subary and UKIRT.
The constraints are based on an abundance matching methodology to the
observational data using cosmological N-body simulations.
The relationship between halo mass and star formation rate follows a
double power law.
We also take into account the influence on the results of the dust extinction
scaling derived from observations by Bouwens et al. (2012).
Taking advantage of a wide dynamical range in observations and
simulations we manage to constrain the free parameters of our model
for halos in the mass range $10^{10}\Msun < M_{h}<10^{13}\Msun$. 
We find that including dust extinction improves the the match with
observations.
Finally, we compare these results against the prediction of abundance matching
methods (to the stellar mass), a semi-analytic model of galaxy
formation (GALFORM) and a hydrodynamical simulation (Illustris).
\end{abstract}

@@

We use 64 cubic boxes of $250$\hMpc on a side to fit the
LF data from \citet{Willott13}.
We use the Likelihood Ratio criterion ($\mathcal{LR}= 0.5$) to
define the $1\sigma$ confidence interval for our parameters.

$M_0$ does not change with and without extinction.
cases (they are compatible within 
the error bars), the turnover point corresponds to the same mass.
$\gamma$ and $L_0$ shown a significative difference in booth cases.
$\beta$ is hard to constraint in booth cases.  
The parameer was limited to vary in the range form 0.0 to 1.6. 
$1\sigma$ region covers the whole range.
